Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

@@

>>>>

\todo{Rahul's result?}

@@

In terms of techniques, our primary contribution is a result on the mathematical structure of the $k$-SJ problem. Specifically, for any $n \ge 1$ and $k \ge 2$, define function $F(n, k)$ to be the lowest value such that any instance of the $k$-SJ problem with input size $n$ and output size $\out$ can be solved in $F(n, k) + O(\out)$ time. Specificaly, define $F(n, 1) = n$ for any $n \ge 1$. Our main technical contribution can now be stated as:

\begin{theorem} \label{thm:main}
    d
\end{theorem}

% To facilitate the description of our finding, let us ``define'' the $k$-SJ problem at $k = 1$ as follows: the input is a set $R$ of $n$ rectangles in $\real^2$, and the objective is to list all the rectangles in $R$. Clearly, this 1-SJ problem can be trivially solved in $O(n)$ time. Our main technical contribution can now be stated as: 
% 
% \boxminipg{0.9\linewidth}{
%     {\bf Main Discovery:} For $k \ge 3$, the $k$-SJ problem can be converted, in $O(n \log n)$ time, to $F_1(k)$ instances of the $(k-1)$-SJ problem and 
% }
